Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses

### 2025-06-30 manuscript_agu.tex
Final edits before the initial submission

The Vaisala CL51 and CT25K (photos in Fig.~\ref{fig:map}d, e) are ceilometers operating at near-infrared wavelengths of 910~nm and 905~nm, respectively. The CL51 can also be configured to emulate the Vaisala CL31. The maximum range is 15.4~km (CL51), 7.7~km (CL31 emulation mode with 5~m vertical resolution), and 7.5~km (CT25K). The vertical resolution is 10~m (5~m configurable) in CL51 and 30~m in CT25K observations. The sampling (temporal) resolution is configurable, and in our datasets, it is approximately 6~s for CL51 on AA15‐16, 16~s for CT25K on MARCUS and MICRE, 36~s for CL51 on RV \emph{Polarstern}, and about 2.37~s for CL51 with CL31 emulation on TAN1502. The wavelengths of 905 and 910~nm are both affected by water vapor absorption of about 20\% in the mid-latitudes \cite{wiegner2015,wiegner2019}, with 910~nm affected more strongly, but we do not expect this to be a significant issue as explained in \citeA{kuma2021}. The instrument data files containing raw uncalibrated backscatter were first converted to Network Common Data Form (NetCDF) with cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF (Section~\ref{sec:alcf}) to produce absolutely calibrated attenuated volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by height, and the total cloud fraction. Because the CT25K uses a very similar wavelength to CL51, equivalent calculations as for CL51 were done assuming a wavelength of 910~nm. The Vaisala CL51 and CT25K instruments were used on most of the voyages and stations analyzed here. Fig.~\ref{fig:example}a shows an example of AVBC derived from the CL51 instrument data.

@@

The RV \emph{Polarstern} datasets are openly available on Pangaea (\url{https://pangaea.de}), as listed in Table~\ref{tab:voyage-references}. The MARCUS and MICRE datasets are openly available from ARM (\url{https://www.arm.gov}). The MERRA-2 data are openly available from the NASA Goddard Earth Sciences (GES) Data and Information Services Center (DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}). The ERA5 data are openly available from the Copernicus Climate Data Store (CDS) (\url{https://cds.climate.copernicus.eu}). The ICON data are available on the Levante cluster of the DKRZ (\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at \url{https://luv.dkrz.de/register/}. The CERES products are openly available from the project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}). The TAN1802 data are openly available on Zenodo \cite{kremser2020}. The code for performing the presented analysis, precipitation detection, and a custom version of the ALCF using for our analysis are open-source and available at \url{https://github.com/peterkuma/icon-so-2024}, \url{https://github.com/peterkuma/alcf-precip}, and \url{https://github.com/peterkuma/icon-so-2024-alcf}, respectively. The remaining voyage data (AA15-16, HMNZSW16, NBP1704, TAN1502, and TAN1702) are openly available on Zenodo \cite{mcdonald2024b}. The Natural Earth dataset is openly available from \url{https://www.naturalearthdata.com}.

>>>>

The Vaisala CL51 and CT25K (photos in Fig.~\ref{fig:map}d, e) are ceilometers operating at near-infrared wavelengths of 910~nm and 905~nm, respectively. The CL51 can also be configured to emulate the Vaisala CL31. The maximum range is 15.4~km (CL51), 7.7~km (CL31 emulation mode with 5~m vertical resolution), and 7.5~km (CT25K). The vertical resolution is 10~m (5~m configurable) in CL51 and 30~m in CT25K observations. The sampling (temporal) resolution is configurable, and in our datasets, it is approximately 6~s for CL51 on AA15‐16, 16~s for CT25K on MARCUS and MICRE, 36~s for CL51 on RV \emph{Polarstern}, and about 2.37~s for CL51 with CL31 emulation on TAN1502. The wavelengths of 905 and 910~nm are both affected by water vapor absorption of about 20\% in the mid-latitudes \cite{wiegner2015,wiegner2019}, with 910~nm affected more strongly, but we do not expect this to be a significant issue as explained in \citeA{kuma2021}. The instrument data files containing raw uncalibrated backscatter were first converted to Network Common Data Form (NetCDF) with cl2nc \cite{kuma2024a} and then processed with the ALCF (Section~\ref{sec:alcf}) to produce absolutely calibrated attenuated volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by height, and the total cloud fraction. Because the CT25K uses a very similar wavelength to CL51, equivalent calculations as for CL51 were done assuming a wavelength of 910~nm. The Vaisala CL51 and CT25K instruments were used on most of the voyages and stations analyzed here. Fig.~\ref{fig:example}a shows an example of AVBC derived from the CL51 instrument data.

@@

The RV \emph{Polarstern} datasets are openly available on Pangaea (\url{https://pangaea.de}), as listed in Table~\ref{tab:voyage-references}. The MARCUS and MICRE datasets are openly available from ARM (\url{https://www.arm.gov}). The MERRA-2 data are openly available from the NASA Goddard Earth Sciences (GES) Data and Information Services Center (DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}). The ERA5 data are openly available from the Copernicus Climate Data Store (CDS) (\url{https://cds.climate.copernicus.eu}). The ICON data are available on the Levante cluster of the DKRZ (\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at \url{https://luv.dkrz.de/register/}. The CERES products are openly available from the project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}). The TAN1802 data are openly available on Zenodo \cite{kremser2020}. The remaining voyage data (AA15-16, HMNZSW16, NBP1704, TAN1502, and TAN1702) are openly available on Zenodo \cite{mcdonald2024b}. The Natural Earth dataset is openly available from \url{https://www.naturalearthdata.com}. The code used in our analysis is open-source and available on Zenodo: the code for performing the presented analysis \cite{kuma2024a}, precipitation detection \cite{kuma2024b}, cl2nc \cite{kuma2024c}, and a custom version of the ALCF used in our analysis \cite{kuma2024d}.
